Implications of uniformly distributed, empirically informed priors for phylogeographical model selection: A reply to Hickerson et al.

### 2014-07-19 manuscripts/reply/reply-acknowledgments.tex
Updating acknowledgments for reply ms.
Adding editor and reviewers.

We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, and Adam Leach\'{e} for
insightful comments that greatly improved this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.

>>>>

We thank Melissa Callahan, Jake Esselstyn, Cameron Siler, Mark Holder, Rafe
Brown, Emily McTavish, Daniel Money, Jordan Koch, Adam Leach\'{e}, Luke Harmon,
and three anonymous reviewers for insightful comments that greatly improved
this work.
We thank Michael Hickerson and co-authors for generously providing their data.
J.\ Oaks and C.\ Linkem thank the National Science Foundation for supporting
this work (DEB 1011423, DBI 1308885 and BIO-1202754).
J.\ Oaks was also supported by the University of Kansas (KU) Office of Graduate
Studies, Society of Systematic Biologists, Sigma Xi Scientific Research
Society, KU Department of Ecology and Evolutionary Biology, and the KU
Biodiversity Institute.
We also thank Mark Holder, the KU Information and Telecommunication Technology
Center, KU Computing Center, and the iPlant Collaborative for the computational
support necessary to conduct the analyses presented herein.
